Topological Equivariance Artist Model

### 2021-03-15 paper/paper.tex
End of math section :)

>>>>

\subsection{Composite and Reusable Artists}
Given the family of artists $(\dtotal_i: i\in I)$ on the same image $+ \coloneqq \underset{i\in I}{\sqcup} \dtotal_{i}$, the + operator defines a simple composition of artists. When artists share a base space $\dbase_2 \hookrightarrow \dbase_1$, a composition operator can be defined such that the the artists can be considered to be acting on different components of the same section. This type of composition is important for creating visualizations where elements need to update together in a consistent way, such as multiple views \cite{alboRadarComparativeEvaluation2016a, hullmanKeeping2018} and brush-linked views\cite{beckerBrushingScatterplots1987,bujaInteractiveData1991}. It is impractical to implement an artist for every single graphic; instead we implement an approximation of an the equivalence class of artists $\{\vartist \in \vartist^{\prime}: \vartist_{1} \equiv \vartist_{2}\}$. Roughly, equivalent artists have the same fiber bundle \vtotal\ and same assembly function \vmark\ but act on different sections \vsection, but we will formalize the definition of the equivalance class in future work.
